\subsection{}
\subsection{Glycemic index, glycemic load, food labels}

\subsection{Sit on click : Bed, piano, washing hands, loo}
Used the sit-on-click when there's only one action to realize with this object and/or when it is the most obvious one.


\subsection{Giving objects}
Brownie, fishing-pole


\subsection{Activities}
-generic skeleton
-how the energy is decreased :checking the animation + on air (?)
-values from litterature for each activity
-an example : walking

\subsection{Food system}
-Energy intake
    *generic skeleton
    *speed
    
-Realistic system :
    A) food need to disappear : 
        1)was a problem : how to add energy continuously if the object that contained the food script died ? 
        2)wait a fixed amount of time (depending on the kind of objects, how long it's supposed to take to eat it) before being destroyed.
        
    B) food animation : the avatar have to seem realistically eating the food item. Thus :
        1) different kind of animations for different kind of food. 3 main animations : eat a normal item, like a cake, drink, or eat like a sandwich.
        2) food orientation issue : it was an important issue... Use a distributor object cf "Giving objects" subsection
    
    C) supporting simultaneous food items eaten when an "active period" can overlapp.
        
\subsection{Insulin related activities}
-created the insulin object : IMAGE : photo, my insulin (big) with builder tool
-created the animation : with Qavimator. Quite long, as anything need to be specified.

-injection of insulin : the model, how energy is lost...



\subsection{Symptoms}
- 
-

\subsection{Non-playing avatars}

